Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey

### 2021-11-03 code/analysis_code/analysisscript.Rmd
.
Part 3 continued. Reorganized the whole "Project" folder".

>>>>

```{r}
data_location <- here::here("data","processed_data","processeddata.rds")
```

#load data. 
```{r}
mydata <- readRDS(data_location)
glimpse(mydata)
```

#The main "outcome variable" is the knowledge of infection status (positive/negative/not tested). There are "predisposing factors" (age, sex, education level, chronic disease history etc), "enabling factors" (socio-economic status, area of residence, source of covid news etc) and "need for care factors" (level of fear of reinfection, quarantined or not). We'll do logistic regression analysis for key factors of epredisposing, enabling and need for care factors.

#We'll start with logistic regression model betweem infection status and Age, Sex, Education level (Key Predisposing Factors)
```{r}
lg_mod <- 
       logistic_reg() %>% 
       set_engine("glm")
lg_fit <-
       lg_mod %>%
       fit(infection_status_info ~ Age + Sex + education, data = mydata)
lg_fit
```

```{r}
tidy(lg_fit)
```

```{r}
lg_fit_table_predisposing <- tidy(lg_fit)
```

# saved it as a file
```{r}
summarytable_file12 = here("results", "lg_fit_table_predisposing.rds")
saveRDS(lg_fit_table_predisposing, file = summarytable_file12)
```

```{r}
glance(lg_fit)
```

```{r}
lg_fit_statistics_predisposing <- glance(lg_fit)
```

# saved it as a file
```{r}
summarytable_file13 = here("results", "lg_fit_statistics_predisposing.rds")
saveRDS(lg_fit_statistics_predisposing, file = summarytable_file13)
```

#Then, we'll do log model betweem infection status and socio economic status, area of residence,student/healthworker, source of covid news (Key enabling Factors)
```{r}
lg_fit1 <-
       lg_mod %>%
       fit(infection_status_info ~ economic_status + residence + trusted_source , data = mydata)
lg_fit1
```

```{r}
tidy(lg_fit1)
```

```{r}
lg_fit_table_enabling <- tidy(lg_fit1)
```

# saved it as a file
```{r}
summarytable_file14 = here("results", "lg_fit_table_enabling.rds")
saveRDS(lg_fit_table_enabling, file = summarytable_file14)
```

```{r}
glance(lg_fit1)
```

```{r}
lg_fit_statistics_enabling <- glance(lg_fit1)
```

# saved it as a file
```{r}
summarytable_file15 = here("results", "lg_fit_statistics_enabling.rds")
saveRDS(lg_fit_statistics_enabling, file = summarytable_file15)
```

#Then, we'll do log model betweem infection status and level of fear of infection and quarantined or not (Key need for care factors )
```{r}
lg_fit2 <-
       lg_mod %>%
       fit(infection_status_info ~ quarantined_or_not + worry_level , data = mydata)
lg_fit2
```

```{r}
tidy(lg_fit2)
```

```{r}
lg_fit_table_needforcare <- tidy(lg_fit2)
```

# saved it as a file
```{r}
summarytable_file16 = here("results", "lg_fit_table_needforcare.rds")
saveRDS(lg_fit_table_needforcare, file = summarytable_file16)
```

```{r}
glance(lg_fit2)
```

```{r}
lg_fit_statistics_needforcare <- glance(lg_fit2)
```

# saved it as a file
```{r}
summarytable_file17 = here("results", "lg_fit_statistics_needforcare.rds")
saveRDS(lg_fit_statistics_needforcare, file = summarytable_file17)
```

#compare three models
```{r}
compare_log_model <- anova(lg_fit$fit, lg_fit1$fit, lg_fit2$fit)
compare_log_model
```

### 2021-11-03 code/analysis_code/exploratory.Rmd
Part 3 continued. Reorganized the whole "Project" folder".

#check if certain column is factor or not
```{r}
is.factor(data1$Sex)
```

>>>>

#MAin outcome variable
```{r}
summary(data1$infection_status_info)
```

#check if certain column is factor or not
```{r}
is.factor(data1$infection_status_info)
```

#plotting infection_status_info count
```{r}
plot1 <- ggplot(data = data1) +
    geom_bar(mapping = aes(x = infection_status_info))
plot1
figure_file = here("results","infection_status_info_distribution.png")
ggsave(filename = figure_file, plot=plot1) 
```

### 2021-11-03 code/processing_code/processingscript.Rmd
Part 3 continued. Reorganized the whole "Project" folder".

```{r}
processeddata <- rawdata %>% rename ("education" = `Highest educational level`,
                               "student/heathworker" = `Are you a student or worker in the healthcare sector?`,
                               "economic_status" = 'Which of the following categories best describes your current socio-economic situation?',
                               "residence" = `Do you live in:`,
                               "trusted_source" = `Which source of COVID-19 information/advice do you trust the most?`,
                               "work_from_home" = 'Are you currently working/studying from home because of the COVID-19 outbreak?',
                               "quarantined_or_not" = `Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`,
                               "infection_status_info" = `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`,
                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,)
```

@@

```{r}
processeddata2 <- processeddata %>%
                  mutate (infection_status_info = factor(infection_status_info)) 
```

```{r}
str(processeddata2)
```

```{r}
save_data_location <- here::here("data","processed_data","processeddata2.rds")
```

>>>>

```{r}
processeddata1 <- rawdata %>% rename ("education" = `Highest educational level`,
                               "student/heathworker" = `Are you a student or worker in the healthcare sector?`,
                               "economic_status" = 'Which of the following categories best describes your current socio-economic situation?',
                               "residence" = `Do you live in:`,
                               "trusted_source" = `Which source of COVID-19 information/advice do you trust the most?`,
                               "work_from_home" = 'Are you currently working/studying from home because of the COVID-19 outbreak?',
                               "quarantined_or_not" = `Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`,
                               "infection_status_info" = `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`,
                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,)
```

```{r}
processeddata<- processeddata1 %>% mutate(across(where(is_character),as_factor))
```

```{r}
View(processeddata)
```

```{r}
str(processeddata)
```

@@

### 2021-11-03 products/manuscript/Manuscript.Rmd
Part 3 continued. Reorganized the whole "Project" folder".

---
title: "Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in nine low-and middle-income countries: an online survey"
subtitle: ""
author: Ehsan Suez
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---

The structure below is a possible setup for a data analysis project (including the course project). For a manuscript, adjust as needed.

# Summary/Abstract
_Write a summary of your project._

@@

_Study design, sample, and procedure_

@@

_Measures_
Using Andersen’s model of health care utilization [Andersen 1995], study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.

_Outcome variable_
COVID-19 testing/infection status will be assessed with the question, “Since the beginning of the COVID-19 outbreak, do you have information on your infection status?” Response options were 1=not tested/does not know test results, 2=negative, and 3=positive.

_Predisposing factors_
Sociodemographic factors included age, sex, country of residence, educational level, and the (estimated) age(s) of their housemate(s). Chronic/underlying diseases includs heart disease, hypertension, diabetes, cancer, HIV, tuberculosis, and chronic asthma; coded as “0” none and “1” at least presence of one clinically diagnosed condition.

_COVID-19 preventive measures_
Participants were asked, “During the past 7 days, have you been observing any of the following preventive measures against COVID-19? 1) Social distancing of at least 1.5m, 2) Wearing a face mask, 3) Hand hygiene (regular handwashing with soap or using hand gel), and 4) Coughing hygiene (covering the mouth when coughing or sneezing). A composite non-adherence to all four COVID-19 preventive measure was calculated by coding each negative response with “1”, summing scores ranging from 0-4 (Cronbach’s alpha 0.7).

_Enabling/disabling factors_
Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.

_Disabling factors_ include the assessment of psychological distress with the Patient Health Questionnaire (PHQ-4) for Depression and Anxiety symptoms [Kroenke/ Löwe]. The severity of psychological distress is categorized as normal (0-2), mild (3-5). moderate (6-8) and severe (9-12) based on the PHQ-4 scores.

_Need for care factors_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.

_Data analysis_

@@

## Data import and cleaning_ [Here I mostly covered descriptive analysis]
---
title: "try"
author: "Ehsan"
date: "10/6/2021"
output: html_document
---

## Exploratory analysis

_Use a combination of text/tables/figures to explore and describe your data. You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data. Depending on the total number of variables in your dataset, explore all or some of the others. FIgures produced here might be histograms or density plots, correlation plots, etc. Tables might summarize your data._

_Continue by creating plots or tables of the outcome(s) of interest and the predictor/exposure/input variables you are most interested in. If your dataset is small, you can do that for all variables. Plots produced here can be scatterplots, boxplots, violinplots, etc. Tables can be simple 2x2 tables or larger ones._

_To get some further insight into your data, if reasonable you could compute simple statistics (e.g. t-tests, simple regression model with 1 predictor, etc.) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._

Table \@ref(tab:summarytable) shows a table summarizing the data.

@@

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like, I just used the generic word `references.bib` but giving it a more descriptive name is probably better.

>>>>

---
title: "Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey"
subtitle: ""
author: Ehsan Suez
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---

# Summary/Abstract
I'll write it later.,

@@

_**Study design, sample, and procedure**_

@@

_**Measures**_
Using Andersen’s model of health care utilization [Andersen 1995], study variables will be categorized into outcome variable, predisposing factors, enabling/disabling factors and need for care factors.

_**Outcome variable**_
COVID-19 testing/infection status will be assessed with the question, “Since the beginning of the COVID-19 outbreak, do you have information on your infection status?” Response options were 1=not tested/does not know test results, 2=negative, and 3=positive.

_**Predisposing factors**_
Sociodemographic factors included age, sex, country of residence, educational level, and the (estimated) age(s) of their housemate(s). Chronic/underlying diseases includs heart disease, hypertension, diabetes, cancer, HIV, tuberculosis, and chronic asthma; coded as “0” none and “1” at least presence of one clinically diagnosed condition.

_**COVID-19 preventive measures**_
Participants were asked, “During the past 7 days, have you been observing any of the following preventive measures against COVID-19? 1) Social distancing of at least 1.5m, 2) Wearing a face mask, 3) Hand hygiene (regular handwashing with soap or using hand gel), and 4) Coughing hygiene (covering the mouth when coughing or sneezing). A composite non-adherence to all four COVID-19 preventive measure was calculated by coding each negative response with “1”, summing scores ranging from 0-4 (Cronbach’s alpha 0.7).

_**Enabling factors**_
Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.

_**Need for care factors**_ include two questions on 1) the level of fear/worry of being infected with COVID-19 (ranging from 1=not at all worried to 5=extremely worried), and 2) having been quarantined (either at home or elsewhere) at any point in time during the COVID-19 epidemic.

_**Data analysis**_

@@

## Data import and cleaning_ html_document
---
```{r}
library(here)
```
## Exploratory analysis

As the infection status information of the participants is the main outcome variable, let's see its distribution among the participants:

```{r resultfigure,  fig.cap='Infection Status Information.', echo=FALSE}
knitr::include_graphics("../../results/infection_status_info_distribution.png")
```

Among the participants, **78.9%** are less than or equal  to 35 years old. That indicates that majority of the participants tend to be younger. While **45.18%** of the participants were female, **54.82%** were male, which shows less chance of biad due to sex. **78.05%** of the participants had a bachelor or post-bachelor degree, clearly indicating that majority of the participants had pretty good education background. Almost **50%** of the participants belongs to "upper middle income category", indicating that at least half of the participants don't belong to the poorer side. Less than **10%** of the participants live in a village/rural area. Health professionals and Tv/radio seems to be the most trusted source to the participants. Apparently equal half of the participants worked from home or not at some stage of the study. Major half of the participants did quarantine at some stage during the study. **63%** of the participants didn't go through a COVID test. Almost half of the participants **(46%)** were moderate or more worried about reinfection. Only **22%** of the participants recorded to have some sort of chronic disease. **(This data can be accessed/viewd through the "supplementary.rmd" file)**

Let's look at the logistic regression analysis and its statistics summary between the **outcome variable** (infection status info) and the three key **predisposing factors** (Age, Sex, Education level).
```{r summarytable12,  echo=FALSE}
resulttable=readRDS("../../results/lg_fit_table_predisposing.rds")
knitr::kable(resulttable, caption = "logistic regression betweem infection status and Key Predisposing Factors")
```

```{r summarytable13,  echo=FALSE}
resulttable=readRDS("../../results/lg_fit_statistics_predisposing.rds")
knitr::kable(resulttable, caption = "logistic regression statistics betweem infection status and Key Predisposing Factors")
```

Next, we want to see the logistic regression analysis statistics between the **outcome variable** (infection status info) and the three key **enabling factors** (socio economic status, area of residence,student/healthworker, source of covid news).

```{r summarytable14,  echo=FALSE}
resulttable=readRDS("../../results/lg_fit_table_enabling.rds")
knitr::kable(resulttable, caption = "logistic regression  betweem infection status and Key Enabling Factors")
```

```{r summarytable15,  echo=FALSE}
resulttable=readRDS("../../results/lg_fit_statistics_enabling.rds")
knitr::kable(resulttable, caption = "logistic regression statistics betweem infection status and Key enabling Factors")
```

Next, we want to see the logistic regression analysis statistics between the **outcome variable** (infection status info) and the level of fear of infection and quarantined or not **(Key need for care factors )**

```{r summarytable16,  echo=FALSE}
resulttable=readRDS("../../results/lg_fit_table_needforcare.rds")
knitr::kable(resulttable, caption = "logistic regression  betweem infection status and Key Need for care Factor")
```

```{r summarytable17,  echo=FALSE}
resulttable=readRDS("../../results/lg_fit_statistics_needforcare.rds")
knitr::kable(resulttable, caption = "logistic regression statistics betweem infection status and Key Need for Care Factors")
```

@@
